---
title: 'Statistical Inference Course Project: Part 2'
author: "Qingxiao Dong"
date: "February 22, 2015"
output:
  html_document: default
  pdf_document:
    keep_tex: yes
  word_document: default
---

This is the project for the statistical inference class (Data Science specialization). The project consists of two parts:

1. A simulation exercise.
2. Basic inferential data analysis. 

Now in the second portion of the class, we’re going to analyze the ```ToothGrowth``` data in the R datasets package.

####1. Load the ToothGrowth data and perform some basic exploratory data analyses 

```{r}
data("ToothGrowth")
data <- as.data.frame(ToothGrowth)
str(data)
```

####2. Provide a basic summary of the data.

```{r}
head(data)
summary(data)
dose<-as.factor(data$dose)
table(data$supp, data$dose)
```

The ToothGrowth dataset explains the relation between the growth of teeth of guinea pigs at each of three dose levels of Vitamin C (0.5, 1 and 2 mg) with each of two delivery methods(orange juice and ascorbic acid).

####3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.

```{r}
# T Test by supplemant type
t.test(len ~ supp, data = ToothGrowth)
# T test by dose level 
Tooth.dose0.5_1.0 <- subset(ToothGrowth, dose %in% c(0.5, 1.0))
Tooth.dose0.5_2.0 <- subset(ToothGrowth, dose %in% c(0.5, 2.0))
Tooth.dose1.0_2.0 <- subset(ToothGrowth, dose %in% c(1.0, 2.0))
t.test(len ~ dose, data = Tooth.dose0.5_1.0)
t.test(len ~ dose, data = Tooth.dose0.5_2.0)
t.test(len ~ dose, data = Tooth.dose1.0_2.0)
# T test for supplement by dose level
Tooth.dose0.5 <- subset(ToothGrowth, dose == 0.5)
Tooth.dose1.0 <- subset(ToothGrowth, dose == 1.0)
Tooth.dose2.0 <- subset(ToothGrowth, dose == 2.0)
t.test(len ~ supp, data = Tooth.dose0.5)
t.test(len ~ supp, data = Tooth.dose1.0)
t.test(len ~ supp, data = Tooth.dose2.0)
```

####4. State your conclusions and the assumptions needed for your conclusions. 

Based of the results, we can say that for doses of ```0.5``` and ```1.0```, OJ has a greater effect on Tooth Growth than VC, we know this by the p.value indicators, which are ```0.0064``` and ```0.001``` respectively, being less than 5% and the confidence intervals of the test do not contain 0. For the test at ```dose == 2.0``` we cannot reject the Ho, as the p.value, which is ```0.064```, is greater than 5% and the confidence test contains 0. For the test OJ vs VC we cannot reject the Ho either, as the p.value is 6% (greater than the 5% threshold used for statiscal analysis) and the confidence interval contains 0.

We can then conclude that to get greater tooth growth with low levels of dosage (0.5 & 1.0) one should use OJ instead of VC. At greater levels (2.0) of dosage it is uncertain whether there will be a greater effect from either OJ or VC.